Check experimental design

### 2023-05-15 analysis/01_experimental-design.Rmd

# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown
# issue1 = emergency
# issue2 = environment
# issue3 = human rights
# issue4 = refugee
# transp1 = not transparent
# transp2 = transparent
# account1 = not accountable
# account2 = accountable
# fund1 = smalldonors
# fund2 = wealthydonors
# fund3 = gov grants
#

# Build out all the necessary interactions...
# ...by multiplying together the needed index-coded levels.
# Sticking exactly to the hypotheses
interactions_exact <- interactions %>% 
  as_tibble() %>% 
  rowwise() %>% 
  mutate(
    # Main Effects
    h1_high = sum(org3, org4), # oxfam and red cross
    h1_low = sum(org1, org2), # amnesty and greenpeace
    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
    h2a_low = gov_rel1, # friendly
    h3a_high = sum(issue1, issue4), # emergency and refugee
    h3a_low = sum(issue2, issue3), # environment and human rights
    h4a_high = fund1, # small donors
    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
    h5a_high = transp2, # transparent
    h5a_low = transp1, # not transparent
    # First Order Interactions
    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
    h4b_high = gov_rel3*fund1, # crackdown * small donors
    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
    # Second Order Interactions
    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
    # Third Order Interaction
    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
  ungroup()

>>>>

# # Build out all the necessary interactions...
# # ...by multiplying together the needed index-coded levels.
# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown
# issue1 = emergency
# issue2 = environment
# issue3 = human rights
# issue4 = refugee
# transp1 = not transparent
# transp2 = transparent
# account1 = not accountable
# account2 = accountable
# fund1 = smalldonors
# fund2 = wealthydonors
# fund3 = gov grants

# interactions <- interactions |> 
#   mutate(
#     # Oxfam or Red Cross.
#     h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
#     # Government crackdown or criticism.
#     h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
#     # Oxfam or Red Cross facing government crackdown or criticism.
#     h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
#     # Amnesty or Greenpeace.
#     h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
#     # Government crackdown.
#     h2b_gov_rel_2 = gov_rel3,
#     # Amnesty or Greenpeace is facing crackdown.
#     # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
#     h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
#   )
#   # select(1:3, contains("h2b"))

# Sticking exactly to the hypotheses
interactions_exact <- interactions %>% 
  as_tibble() %>% 
  rowwise() %>% 
  mutate(
    # Main Effects
    h1_high = sum(org3, org4), # oxfam and red cross
    h1_low = sum(org1, org2), # amnesty and greenpeace
    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
    h2a_low = gov_rel1, # friendly
    h3a_high = sum(issue1, issue4), # emergency and refugee
    h3a_low = sum(issue2, issue3), # environment and human rights
    h4a_high = fund1, # small donors
    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
    h5a_high = transp2, # transparent
    h5a_low = transp1, # not transparent
    # First Order Interactions
    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
    h4b_high = gov_rel3*fund1, # crackdown * small donors
    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
    # Second Order Interactions
    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
    # Third Order Interaction
    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
  ungroup()
